%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[includefoot]{mcdowellcv}

% Override cls file to show page numbers
\pagestyle{plain}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Milton Inostroza}
\address{11133 NE 109th Lane, M101 \linebreak Kirkland WA 98033}
\contacts{+1 (312) 307-9187 \linebreak minostro@minostro.com}

\begin{document}
	% Print the header
	\makeheader
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Staff Software Engineer}{Block Inc, Remote, USA}{2024 -- Present}
			\strong{Block, Local Team}
			\begin{itemize}
				\item Part of a small team of senior engineers tasked with building "Local" a product that connects Square sellers with Cash App customers. A key contribution that accelerated the time to market was developing a pragmatic, "good enough" solution to handle sending cash back to buyers whenever they transacted with a seller. This approach saved several months of development time, significantly reducing the go-to-market timeline and enabling faster validation of the product. 
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Staff Software Engineer}{Block Inc, Remote, USA}{2019 -- 2023}
			\strong{Cash App, Investing Team}  
			\begin{itemize}
				\item Led the Stock/Bitcoin Gifting project, one of the first of its kind in the industry, enabling Cash App customers to send and receive various asset types seamlessly. I architected the technical solution for how the investing team would support the project while simultaneously acting as a liaison, leading a cross-functional working group of 7 teams to ensure alignment on technical decisions and secure the necessary support. One of my most impactful contributions was influencing the design of the new P2P infrastructure to support multiple asset types beyond fiat, shaping the foundation for future innovations. Additionally, I strategically broke down the project execution to test the initial concept in the market without requiring a full infrastructure overhaul, accelerating go-to-market by approximately 6 months, reducing risk, and enabling faster customer feedback.
				\item Led the migration of critical investing-related components from the Cash App monolith, significantly improving the reliability and availability of the investing product. Our team was one of the first to initiate and successfully complete this complex migration, setting a strong precedent for other teams. I played a pivotal role in crafting detailed migration plans that prioritized delivering value to customers early and developing reusable migration recipes that streamlined the process for other teams. These contributions not only accelerated the overall migration effort but also established best practices for future initiatives.
				\item Served as a consultant software architect for the Teen Investing project, enabling teens to gain exposure to the stock market in a safe and seamless manner. Leveraging my deep knowledge of the Cash App ecosystem, I guided the team on key technical decisions, ensuring alignment with best practices and long-term scalability. A pivotal contribution was suggesting the development of a bridge component that allowed the team to reuse existing business logic still residing in the Cash App monolith, effectively reducing the go-to-market timeline by approximately 4 months.   
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Senior Software Engineer}{Groupon Inc, Remote, USA}{2018 -- 2019}
			\strong{Card Link Offers Team} -- Java8; Ruby; PostgresSQL; Redis; Sidekiq; Splunk; Blazemeter--
			\begin{itemize}
				\item Card Interaction Service is in charge of registering credit cards and receiving transactional data from the Credit Card Providers (VISA, MasterCard and Amex). I led the design/implementation of this service. I interacted closely with the MasterCard and Amex Product/Engineering teams to ensure the success of the project. 
			 	\item Targeted Offers project is meant to decrease Merchant Attrition. I led the design of the system by interacting closely with the Business/Product teams. One interesting technical challenge I solved was to improve the latency of the Product\#fetch endpoint (from 200ms to 10ms) and increased the throughput to 180K rpm.
				\item Mentored Software Engineers. Two of them got promoted from Junior to Mid-Level.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Full Stack Software Engineer}{Groupon Inc, Seattle}{2017}
			\strong{Things To Do Team} -- JavaScript; Ruby; NodeJS; MySQL --
			\begin{itemize}
			 	\item Led the implementation of Front End module to allow customers to buy multiple inventory in one transaction. 
				\item Wrote the proposal to stop using JQuery in favor of Vanilla Javascript. This was adopted Groupon-wide. 
				\item Modified the Things-To-Do Inventory Service to improve the latency of an endpoint (from 600ms to 20ms) and to increase the throughput to 100K rpm.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Backend Software Engineer}{Groupon Inc, Chicago}{2013 -- 2016}
			\strong{Global Finance Engineering Team} -- Ruby; Ruby on Rails; Clojure; MySQL; Memcached; Redis; Resque --
			\begin{itemize}
				\item Led the process of adding Geo Redundancy support to 10 services (Global Financial Infrastructure).
				\item Built the Audit System to ensure that the new and legacy ledger agree on transactions accounted for contracts.
				\item Built the VAT Invoicing Service (13 EMEA Countries), reducing the processing time from 3 days to ~12 hours.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Backend Software Engineer}{Groupon Inc, Santiago, Chile}{2012 -- 2013}
			\strong{LATAM Finance Engineering Team} -- PHP; CakePHP; MySQL; Java SE --
			\begin{itemize}
				\item Built the integration between the LATAM (6+ countries) platform and the Global Ledger System (Netsuite).
				\item Built the Tax Retention System for Argentinian and Colombian Partners.
			\end{itemize}
		\end{cvsubsection}		
		\begin{cvsubsection}{Software Engineer}{Contractor, Chile}{2005 -- 2008}
		        \strong{Meaculpas, Liquor Store Chain} -- Python; Django; PyGTK+; JavaScript; PostgreSQL --
			\begin{itemize}
				\item Led the development of the Points of Sales (7+ branches) and the Management platform of the business.
				\item Led the implementation of RemuneX: A Payroll System for 100+ employees.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Santiago, Chile}{Universidad de Chile}{March 2010 --  April 2013}
			\begin{itemize}
				\item M.S.E. in Computer Science, April 2013; Thesis: Safe and Practical Decoupling of Aspects with Joint Point Interfaces. Published in ACM Transactions on Software Engineering and Methodology, 2014.
			\end{itemize}
		\end{cvsubsection}
%		\begin{cvsubsection}{Iquique, Chile}{Universidad Arturo Prat}{March 2001 --  December 2007}
%			\begin{itemize}
%				\item B.S.E. in Computer Science, December 2005; Software Engineer, December 2007.
%			\end{itemize}
%		\end{cvsubsection}
	\end{cvsection}
	
%	\begin{cvsection}{Technical Experience}
%		\begin{cvsubsection}{Projects}{}{}
%			\begin{itemize}
%				\item \textbf{Poolmachine} (2014) An Erlang OTP Application that manages pools of workers. Personal project.
%				\item \textbf{Joint Point Interfaces for AspectJ} (2011). Extended the AspectBench Compiler for AspectJ to implement Joint Point Interfaces. AspectJ is an aspect-oriented programming language for Java.
%			\end{itemize}
%		\end{cvsubsection}
%	\end{cvsection}
	
	\begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
			        \item \textbf{Privacy Champion:} Advocate for best practices and compliance of General Data Protection Regulation (GDPR), Groupon, 2018.
			        \item \textbf{Erlang Interest Group:} Led bi-weekly meetings to talk/learn about Erlang. Group conformed by 10 software developers, Groupon, Chicago, 2016.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Kotlin; Ruby; Java8; JavaScript; SQL; Python; Clojure; PHP; AspectJ; Erlang 
				\item Misk; Ruby on Rails; Django; MySQL; PostgreSQL; Redis; Memcached; NodeJS; CakePHP; Sidekiq; Resque; Splunk; Blazemeter; Datadog; Kafka
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\end{document}
